Summer 2025 ToDo

### 2025-07-08 Relations/Paper/Summer_2025_TODO.tex
Implications and summertodo minor changes update

\section*{Week starting April 28th}
\begin{itemize}
  \item Below notes from meeting on April 25th.
  \begin{todolist}
    \item Fix Wellfounded.agda after changes made during meeting.
    \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
    \item Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
    \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
    \item (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers.
    \item (Research item) Find a concrete application of generalized Newman's Lemma.
    \item (Research item) Use TeReSe to create a list of rewrite systems.
    \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section.
    \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was).
    \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
    \item (Research item) Do we want to reincorporate Knaster Tarski?
  \end{todolist}

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item Remove "desired implications" and similar organizational issues in the code (general review)
  \item Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}

>>>>

\section*{Week starting April 28th}
\begin{itemize}
  \item Below notes from meeting on April 25th.
  \begin{todolist}
    \item  Fix Wellfounded.agda after changes made during meeting.
    \item Carry on refactoring Wellfounded.agda once fixed, breaking it up if necessary.
    \item [\done] Think about how to organize the Git repo going forward. For example, could be good to have a parent folder with ARS and WF, with a private dir for paper
    \item (Research item) How to go from WFseq to WFacc - possible that the Kleene Tree is a solution.
    \item (Research item) Go deeper in the related works and see which are most relevant. Make a list of works and give summaries to be used in future papers.
    \item (Research item) Find a concrete application of generalized Newman's Lemma.
    \item (Research item) Use TeReSe to create a list of rewrite systems.
    \item (Research item) Work on the missing implicaitons from the paper. So far we believe this is just CR $\to$ CP in the ARS section.
    \item (Research item) Formalize a first order term rewriting system (I can't remember what the motivation for this was).
    \item (Research item) Carry out research on rewriting counterexamples like our own so we can try and put them into some sort of context. Have our counerexamples been shown before?
    \item (Research item) Do we want to reincorporate Knaster Tarski?
  \end{todolist}

\end{itemize}
\section*{Week starting 26th May}
\begin{todolist}
  \item Double check the counterexamples match in the table to the diagrams.
  \item [\done] Make clear in proof references to agda code how it should be read (especially the first one). Make clear the module as well. After doing once, the others don't need to be as explicit.
  \item [\done] find a seperate symbol for -> in the code sections in the paper for UN$\to$. Superscipt would be perfect. $UN^{\rightarrow}$
  \item [\done] Mention theorem 123 ii and iii are inherently classical. For iii we require strong decidability.
  \item [\done] Working on CR $\to$ CP. Low priority. \apcomment{This is mentioned as one of the research items above}
\end{todolist}

\section*{Week starting 2nd June}
\begin{todolist}
  \item [\done] Should we add quantification to each definition(I think quantification for $a$ is already implied)? E.g.\\
  \item [\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.\\
   Transforms to
  \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$ for all $b, c, d \in A$.
  \item [\done] For showing inc -> RP we're currently just saying "This is immediate". Is this sufficient? We did have a proof previously but I think we removed it for space reasons.
  \item [\done] Remove "desired implications" and similar organizational issues in the code (general review)
  \item [\done] Consider defining FB in terms of existing list library; especially in the rebooted repo,
  we shouldn't use manual List type just for this.
  \item [\done] Move all definitions and properties from Section 2.3 to Seq.agda, except Inc.
  \item [\done] Revise section 3.1
\end{todolist}
\section*{Week starting 9th June (some of these items taken from Dr. Polonsky's email sent June 6th)}
\begin{todolist}
  \item [\done] Thm. 19(iv), i don't like that the parens are italicized.  maybe it would be okay if instead of CR => CP we just write "the forward implication"
  \item [\done] Proof of (iii), line 296: do we really need () around SN?
  \item Page 9, second half (the hierarchy): we should add a proof that $\MF \cap \SN \iff \NF$, say this in the text, and note that this does NOT hold for $\SM$ and $\WN$.  Hence, the tables include a separate column for their combination.
  \item  In the par before 4.1 counterexamples, add that in the global table, the counterexample 3 satisfies the hypotheses globally.
(I actually wonder whether we need example 9 at all, if we have a counterexample to the global one.  Am I missing something?). \sacomment{I don't think we need to expand that CE:3 satisfies the global hypotheses. I'm hoping that we've done enough to show to the reader how to read the table at this point. If you disagree I'm happy to add it in though. As to why have local and global counterexamples, good point. Unless either of us can think of a reason we'll remove in the next meeting.}
    \item [\done] the * and dagger in the table should be explained in the caption, or in the text.
    \sacomment{I prefer to have this as a footnote. I have put it as a caption for now but I would revert it to what we had before.  }
\end{todolist}
